To conclude, we studied gapped fractional topological insulator surface states with (i) time reversal breaking order, (ii) charge $U(1)$ breaking order, as well as (iii) symmetry preserving generalized $\mathcal{T}$-Pfaffian topological order. We focused on fractional topological insulator that supported fractionally charged partons coupling with a discrete $\mathbb{Z}_{2n+1}$ gauge theory. We characterized the fractional interface channels sandwiched between different gapped surface domains by describing their charge and energy response, namely the differential electric and thermal conductance. The low-energy conformal field theory for these fractional interface channels corresponded to the topological order of quasi-$(2+1)$-D fractional topological insulator slabs with the corresponding gapped top and bottom surfaces. In particular, a fractional topological insulator slab with time reversal conjugate ferromagnetic surfaces behaved like a fractional Chern insulator with topological order \eqref{FTIFSFS}, and in the particular case when $a=-1$ and $g=-2$, its charge sector was identical to that of the Laughlin $\nu=1/(2n+1)$ fractional quantum hall state. Combining the time reversal symmetric generalized $\mathcal{T}$-Pfaffian surface with the fractional topological insulator bulk as well as the opposite time reversal breaking surface, this fractional topological insulator slab exhibited a generalized Pfaffian topological order \eqref{ZfTO}. Furthermore, we demonstrated the gluing of a pair of parallel generalized $\mathcal{T}$-Pfaffian surfaces, which are supported by two fractional topological insulator on both sides. It was captured by an anyon condensation picture that killed the generalized $\mathcal{T}$-Pfaffian topological order and left behind deconfined partons and confined gauge and magnetic monopoles in the bulk. 

In Ref.~\cite{ChoTeoFradkin17} we also construct the generalized $\mathcal{T}$-Pfaffian state of the fractional topological insulator from the field theoretic duality approach.