The chiral channel $\mathcal{F}$ in \eqref{FTIFSFS} between a pair of time reversal conjugate ferromagnetic surface domains divides into a pair of fermionic $\mathrm{Pf}^\ast$ in \eqref{ZfTO} at a junction where the two ferromagnetic surface domains sandwich a time reversal symmetric generalized $\mathcal{T}$-Pfaffian surface domain (see Fig.~\ref{fig1}). Conservation of charge and energy requires the filling fractions and chiral central charges to equally split, i.e.~$2\nu_{\mathrm{Pf}^\ast}=\nu_{\mathcal{F}}$ and $2c_{\mathrm{Pf}^\ast}=c_{\mathcal{F}}$. For instance, in the prototype case when $a=-1$ and $g=-2$, $\nu_{\mathrm{Pf}^\ast}=1/2(2n+1)$ and $c_{\mathrm{Pf}^\ast}=(2n+1)/2$. Similar to the aforementioned $\mathcal{F}$ case, these quantities are subjected to surface reconstruction $\nu\to\nu+N$, $c\to c+N$. %for an arbitrary integer $N$ when $\theta$ is fixed. 

In addition to the response quantities, the topological order of $\mathcal{F}$ for the fractional topological insulator slab with time reversal conjugate ferromagnetic surface is related to that of the fermionic $\mathrm{Pf}^\ast$ by a {\em relative tensor product} \begin{align}\mathcal{F}=\mathrm{Pf}^\ast\boxtimes_b\mathrm{Pf}^\ast.\label{gluing}\end{align} This can be understood by juxtaposing the time reversal symmetric surfaces of a pair of $\mathrm{Pf}^\ast$ fractional topological insulator slabs and condensing surface bosonic anyon pairs on the two generalized $\mathcal{T}$-Pfaffian surfaces. This anyon condensation~\cite{BaisSlingerlandCondensation,Kong14,NeupertHeKeyserlingkSierraBernevig16} procedure effectively glues the two fractional topological insulator slabs together along the time reversal symmetric surfaces  (see Fig.~\ref{fig1}). The relative tensor product $\boxtimes_b$ involves first taking a decoupled tensor product $\otimes$ when the two $\mathrm{Pf}^\ast$ fractional topological insulator slabs are put side by side, and then condensing a set b of bosons. The anyons of the decoupled tensor product takes the form $\tilde{X}^A_{j,z}\otimes\tilde{X}^B_{j',z'}$, where $A,B$ refers to the two slabs. 
Our set b consists of electrically neutral anyons in the subset $(\mathcal{T}$-$\mathrm{Pf}^\ast)^A\otimes(\mathcal{T}$-$\mathrm{Pf}^\ast)^B$ where $A,B$ refers to the two slabs in order to preserve symmetries. Now we look into exactly which bosons we should condense.

First notice that dyon combinations $\gamma^z\equiv \tilde\openone^A_{0,z}\tilde\openone^B_{0,z}$ are not confined. A particle with charge ``$j$'' has gauge charge $n^2gj$, so any neutral pairs have gauge charge $n^2gj \otimes -n^2gj$. Thus the braiding phase with these dyons is $zn^2gj-zn^2gj = 0$.

Our parton should continuously move from slab $A$ to slab $B$, so we should condense $\Psi^A_{4}\Psi^B_{-4}$, the parton creation annihilation operator. Anything that braids with it is confined. We can derive braiding statistics once more with the ribbon formula, $\theta_{A,B}=h_{A \times B}-h_A-h_B$. The braiding phase from the anyon combination $\tilde{X}^A_{j_a,z_a}\tilde{X}^B_{j_b,z_b}$ around $\Psi^A_{4}\Psi^B_{-4}$ is is the same as $(\delta^A)^{z_a+n^3ugj_a}(\delta^B)^{z_b+n^3ugj_b}$ around $\Psi^A_{4}\Psi^B_{-4}$, since these are just the dyonic parts of $\tilde{X}^A_{j_a,z_a}\tilde{X}^B_{j_b,z_b}$ from definition \ref{Zfanyon}. The parton carries ``$g$'' gauge charge so this phase is  $g(z_a+n^3ugj_a-z_b-n^3ugj_b)$. This is zero if the dyon number $z+n^3ugj$ is equal on the $A$ and $B$ particle. This ensures gauge fluxes must continue through both $A$ and $B$ slabs, i.e., confines gauge magnetic monopoles. This means that we are left with combinations ${X}^A_{j_a}{X}^B_{j_b}\gamma^z$. It also identifies $\Psi^A_{4}\Psi^B_{-4}$ with the vacuum, which identifies 
\
\begin{align*}
\openone^A_{j_a}\openone^B_{j_b}\gamma^z&\equiv\Psi^A_{j_a+4}\Psi^B_{j_b-4}\gamma^z \equiv\openone^A_{j_a+8}\openone^B_{j_b-8}\gamma^z, \\
\openone^A_{j_a}\Psi^B_{j_b}\gamma^z&\equiv\Psi^A_{j_a+4}\openone^B_{j_b-4}\gamma^z \equiv\openone^A_{j_a+8}\Psi^B_{j_b-8}\gamma^z, \\
\Sigma^A_{j_a}\Sigma^B_{j_b}\gamma^z&\equiv\Sigma^A_{j_a+4}\Sigma^B_{j_b-4}\gamma^z, \\
\openone^A_{j_a}\Sigma^B_{j_b}\gamma^z&\equiv\Psi^A_{j_a+4}\Sigma^B_{j_b-4}\gamma^z \equiv\openone^A_{j_a+8}\Sigma^B_{j_b-8}\gamma^z\\
&\equiv\Psi^A_{j_a+12}\Sigma^B_{j_b-12}\gamma^z.
\end{align*}

Next we choose the fermion pair $\Psi_0^A \times \Psi^B_0$. Notice $\Sigma$ braids with $\Psi$, so anything with just one $\Sigma$ is confined. This brings the identification to

\begin{align*}
&\openone^A_{j_a}\openone^B_{j_b}\gamma^z  \equiv\openone^A_{j_a+4j}\openone^B_{j_b-4j}\gamma^z  \equiv\Psi^A_{j_a+4j}\Psi^B_{j_b-4j}\gamma^z, \\
&\openone^A_{j_a}\Psi^B_{j_b}\gamma^z  \equiv\openone^A_{j_a+4j}\Psi^B_{j_b-4j}\gamma^z \equiv\Psi^A_{j_a+4j}\openone^B_{j_b-4j}\gamma^z, \\
&\Sigma^A_{j_a}\Sigma^B_{j_b}\gamma^z\equiv\Sigma^A_{j_a+4j}\Sigma^B_{j_b-4j}\gamma^z. 
\end{align*}

Next we can condense $\Psi^A_{2}\openone^B_{-2}$, which when braided around $\openone^A_{j_a}\openone^B_{j_b}$ or $\Psi^A_{j_a}\openone^B_{j_b}$  gives $4(j_a-j_b)/16$ which is not confined if $j_a-j_b=0$ mod 4. For $\Sigma^A_{j_a}\Sigma^B_{j_b}$  gives $4(j_a-j_b)/16+1/2$ which is not confined if $j_a-j_b=2$ mod 4. The identification is now

\begin{align*}
\openone^A_{j_a}\openone^B_{j_b}\gamma^z&\equiv\openone^A_{j_a+4j}\openone^B_{j_b-4j}\gamma^z\equiv\Psi^A_{j_a+4j}\Psi^B_{j_b-4j}\gamma^z\\ &\equiv\openone^A_{j_a+2}\Psi^B_{j_b-2}\gamma^z\equiv\openone^A_{j_a+2+4j}\Psi^B_{j_b-2-4j}\gamma^z 
\\&\equiv\Psi^A_{j_a+2+4j}\openone^B_{j_b-2-4j}\gamma^z, \\
\Sigma^A_{j_a}\Sigma^B_{j_b}\gamma^z&\equiv\Sigma^A_{j_a+2j}\Sigma^B_{j_b-2j}\gamma^z.
\end{align*}

Our $\Sigma \Sigma$ pairs now split into simpler Abelian components
\
\begin{align}\Sigma^A_{j_a\pm1}\Sigma^B_{j_b\mp1}=S^+_{j_a\pm1,j_b\mp1}+S^-_{j_a\pm1,j_b\mp1},\end{align}
\
\noindent
where each $S^\pm$ carries the same spin as the original Ising pair but differs from each other by a unit fermion $S^\pm\times\Psi^{A/B}=S^\mp$. $S^+$ and $S^-$ normally have non-trivial mutual monodromy. We choose to condense the electrically neutral $S^+_{1,-1}$ and its multiples, while confining  $S^-_{1,-1}$. This means $\Sigma^A_{1}\Sigma^B_{-1}$ is condensed/confined. The $\Sigma$ pair around $\openone^A_{j_a}\openone^B_{j_b}$ gives a phase of $2(j_a-j_b)/16$ which is zero if $j_a-j_b=0$ mod 8. The $\Sigma$ pair around $\openone^A_{j_a}\Psi^B_{j_b}$ gives a phase of $2(j_a-j_b)/16+1/2$ which is zero if $j_a-j_b=4$ mod 8. The $\Sigma$ pair around $\Sigma^A_{j_a}\Sigma^B_{j_b}$ gives a phase of $2(j_a-j_b)/16\pm1/4$ which is zero if $j_a-j_b=2$ or $6$ mod 8.


This then completes the full condensate, and we have the identification
\begin{align}
\openone^A_{j_a}\openone^B_{j_b}\gamma^z&\equiv\Psi^A_{j_a,z}\Psi^B_{j_b,z}\gamma^z\equiv\Psi^A_{j_a+2}\openone^B_{j_b-2}\gamma^z\nonumber\\&\equiv\openone^A_{j_a+2}\Psi^B_{j_b-2,z}\gamma^z\equiv S^\pm_{j_a\pm1,j_b\mp1}\gamma^z\nonumber\\&\equiv\openone^A_{j_a+4}\openone^B_{j_b-4}\gamma^z\label{bulk2}
\end{align}
for $j_a\equiv j_b$ mod 8 and $j_a,j_b$ both even. This ends up being just the multiples of the parton $\openone^A_{0}\Psi^B_{4}$ together with the dyons $\gamma^z$. Together they generate the theory $\mathcal{F}$ of a FTI slab with two conjugate TR breaking surfaces. At the end of this calculations our set b of condensed bosons is 
\begin{align}b=\left\{\begin{array}{*{20}c}\openone^A_{4j}\openone^B_{-4j},\Psi^A_{4j}\Psi^B_{-4j},\openone^A_{4j+2}\Psi^B_{-4j-2},\\\Psi^A_{4j+2}\openone^B_{-4j-2},\Sigma^A_{2j+1}\Sigma^B_{-2j-1}\end{array}\right\}.\label{bosons}\end{align} Physically, we have just ensured gauge fluxes and partons must continue through both $A$ and $B$ slabs.

Equation~\eqref{bulk2} are just parton combinations. For instance, $\psi^A=\Psi^A_4\openone^B_0\equiv\openone^A_4\Psi^B_4=\psi^B$ are now free to move inside both fractional topological insulator slabs after gluing. The topological order after the gluing is generated by the partons and dyons, which behave identically to those in $\mathcal{F}$ of \eqref{FTIFSFS}. This proves \eqref{gluing}. The anyon condensation gluing of the pair of generalized $\mathcal{T}$-Pfaffian states preserves symmetries for the same reason it does for the conventional topological insulator case~\cite{ChenFidkowskiVishwanath14,ChoTeoFradkin17}.

It is worth noting that a magnetic monopole can be mimicked by a magnetic flux tube / Dirac string (with flux quantum $hc/e$) that originates at the time reversal symmetric surface interface and passes through one of the two fractional topological insulator slab, say the $A$ slab. In the prototype $a=-2$ and $g=-1$, the filling fraction $\nu_{\mathrm{Pf}^\ast}=1/2(2n+1)$ of the quasi-two-dimensional slab ensures, according to the Laughlin argument~\cite{Laughlin_IQHE}, that the monopole associates to the fractional charge $q=1/2(2n+1)$, which is carried by the confined generalized $\mathcal{T}$-Pfaffian surface anyons $\openone^A_2$ or $\Psi^A_2$. This surface condensation picture therefore provides a simple verification of the Witten effect~\cite{Witten79} for $\theta=\pi/(2n+1)$. 

Lastly, we noticed that in the band insulator case for $n=0$, $\mathcal{F}$ in \eqref{FTIFSFS} reduces to the Chern insulator or the lowest Landau level, and $\mathrm{Pf}^\ast$ in \eqref{ZfTO} is simply the particle-hole symmetric Pfaffian state~\cite{Son15,BarkeshliMulliganFisher15,WangSenthil16}. The particle hole symmetry is captured by the relative tensor product \eqref{gluing}, which can be formally rewritten into \begin{align}\mathrm{Pf}^\ast=\mathcal{F}\boxtimes\overline{\mathrm{Pf}^\ast}\label{gluing2}\end{align} by putting $\mathrm{Pf}^\ast$ on the other side of the equation. Here, the tensor product is relative with respect to some collection of condensed bosonic pairs, and $\overline{\mathrm{Pf}^\ast}$ is the time reversal conjugate of $\mathrm{Pf}^\ast$. Equation~\eqref{gluing2} thus equates $\mathrm{Pf}^\ast$ with its particle hole conjugate, which is obtained by subtracting itself from the lowest landau level. In the fractional case with $n>0$, \eqref{gluing2} suggests a generalized particle hole symmetry for $\mathrm{Pf}^\ast$, whose particle hole conjugate is the subtraction of itself from the fractional quantum hall state $\mathcal{F}$.