\begin{acknowledgments}
The following research would not have been possible without the help of many people. First and foremost I thank my advisor, Prof. Jeffrey C.Y. Teo. His guidance and bright ideas provided the bulk of the inspiration for the work below, and many of his inventive solutions surmounted many seemingly impassable roadblocks. Training under him taught me the value of creativity, patience, diligence, and optimism in traversing the highly nonlinear road that is research. His teaching has become a model for me. I am proud to have studied under his tutelage for so long.

I thank Maria Vucelja, Diana Vaman, Harry Thacker, and Craig Dukes for countless conversations exploring other captivating fields of physics. I thank my thesis committee members for taking the time and energy to review my work, and give me valuable feedback. I thank all of my professors, such as Peter Arnold, and Michael Fowler for showing me just how well a job can be done. I'd like to thank the countless individuals whom my research is based upon, since it is only by standing on the shoulders of giants that I was able to write this modest manuscript.

I owe much of this to my colleagues Syed Raza, Sharmitha Sahoo, and Meng Hua who struggled with me, and challenged me to keep pace. I owe much of my ambition to them.

I would like to thank Richard Marshall, Maksym Bychkov, and Atsushi Yoshida for whom I taught, which helped teach me how little I know, and how difficult the art of communication can be.

Last but not least I would like to thank my friends and family, Camille Silva, Daniel Smith, Austin Husson, Cameron Mankin, Guillaume Bailey, Marybeth Beydler, my mother, my father, and my siblings, for their support and for keeping me motivated these past 5 years. I would not be here without them.
	
This work is supported by the NSF under Grant No.~DMR-1653535, and Grant No.~DMR-1653535. 

\end{acknowledgments}